---
title: "Homework 1"
author: "Mia Guarnieri"
date: "2023-01-18"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(deSolve)
library(ggplot2)
```

#Part 1

##Set up functions

Estimate instantaneous growth rate

```{r cars}
gs_dat <- data.frame(week = c(0, 6, 9), slime = c(10, 40, 80))
lm(log(slime) ~ week, data = gs_dat)
```

Simulate the model

```{r}
#Define the model as a function
Exponential <- function(t, state, parameters) {
with(as.list(c(state, parameters)), {
dN <- r * N
list(c(dN))
})
}

#Define the state variables, parameters, and times

parameters <- c(r = 0.23)
state <- c(N = 3) # We specify the initial values here
times <- 0:10 # Can use seq() to generate non-integer output times

#Run and save the model

exponential_sim <- ode(y = state, times = times, func = Exponential, parms = parameters)

exponential_sim
```


Build a model that includes harvest

```{r}
#Define the model as a function
Exponential_harvest <- function(t, state, parameters) {
with(as.list(c(state, parameters)), {
if (N > 0) {
dN <- r * N - h
} else {
dN <- 0
}
list(c(dN))
})
}

#Define the state variables, parameters, and times

parameters <- c(r = 0.23/7, h = 1)
state <- c(N = 15)
times <- 0:20 # this is now time in days!

#Run and save the model

exp_harvest_sim <- ode(y = state, times = times, func = Exponential_harvest, parms = parameters)

exp_harvest_sim

#Plot the model

ggplot(aes(x = time, y = N), data = as.data.frame(exp_harvest_sim)) + 
  geom_line()
```

If harvest costs double on weekends:

```{r}
#Set up the model function
Exponential_harvest_wknd <- function(t, state, parameters) {
with(as.list(c(state, parameters)), {
if (N > 0) {
if (t %% 7 < 5) {
dN <- r * N - h
} else {
dN <- r * N
}
} else {
dN <- 0
}
list(c(dN))
})
}

#Run the model

times <- 0:40
exp_harvest_wknd_sim <- ode(y = state, times = times, func = Exponential_harvest_wknd, parms = parameters)


#Plot the model

ggplot(aes(x = time, y = N), data = as.data.frame(exp_harvest_wknd_sim)) + geom_line()
```

##Scenario 1: We request the full amount of funding up front

It will take 9 weeks from the day you are submitting the proposal until the day that the contractor would begin to clear the slime.

```{r}
#Exponential model function
Exponential <- function(t, state, parameters) {
with(as.list(c(state, parameters)), {
dN <- r * N
list(c(dN))
})
}

#Define the state variables, parameters, and times

parameters <- c(r = 0.23)
state <- c(N = 3) # We specify the initial values here
times <- 0:9 #9 weeks

#Run and save the exponential

exponential_sim_s1 <- ode(y = state, times = times, func = Exponential, parms = parameters)

starting_area_s1 <- as.numeric(exponential_sim_s1[10,2])

#Growth with harvest, harvest would start after week 9 - this is if the contractor works weekends

Exponential_harvest <- function(t, state, parameters) {
with(as.list(c(state, parameters)), {
if (N > 0) {
dN <- r * N - h
} else {
dN <- 0
}
list(c(dN))
})
}

#Define the state variables, parameters, and times

parameters <- c(r = 0.23/7, h = 1)
state <- c(N = starting_area)
times <- 0:50 # this is now time in days!

#Run and save the model

exp_harvest_sim_s1 <- ode(y = state, times = times, func = Exponential_harvest, parms = parameters)

exp_harvest_sim_s1

ggplot(aes(x = time, y = N), data = as.data.frame(exp_harvest_sim_s1)) + geom_line()


#Growth with harvest, harvest would start after week 9 - this is if the contractor does not work weekends

Exponential_harvest_wknd <- function(t, state, parameters) {
with(as.list(c(state, parameters)), {
if (N > 0) {
if (t %% 7 < 5) {
dN <- r * N - h
} else {
dN <- r * N
}
} else {
dN <- 0
}
list(c(dN))
})
}

#Run the model

parameters <- c(r = 0.23/7, h = 1)
state <- c(N = starting_area)
times <- 0:50 # this is now time in days!

exp_harvest_wknd_sim_s1 <- ode(y = state, times = times, func = Exponential_harvest_wknd, parms = parameters)

exp_harvest_wknd_sim_s1

#Plot the model

ggplot(aes(x = time, y = N), data = as.data.frame(exp_harvest_wknd_sim_s1)) + geom_line()

```

Results: It takes 46 days to clear the slime if the contractor works weekends, and isn't possible to clear if they don't work weekends. This is about 6.5 weeks, so 12 weekend days and 34 weekdays. The total cost would be $58,000.

##Scenario 2: We request up to or less than $10,000 initially, to start removal right away.

It would take 2 weeks to obtain up to $10,000

```{r}
#Exponential model function
Exponential <- function(t, state, parameters) {
with(as.list(c(state, parameters)), {
dN <- r * N
list(c(dN))
})
}

#Define the state variables, parameters, and times

parameters <- c(r = 0.23)
state <- c(N = 3) # We specify the initial values here
times <- 0:2 #2 weeks

#Run and save the exponential

exponential_sim_s2 <- ode(y = state, times = times, func = Exponential, parms = parameters)

starting_area_s2 <- as.numeric(exponential_sim_s2[3,2])

#Growth with harvest, harvest would start after week 2 - this is if the contractor works weekends

Exponential_harvest <- function(t, state, parameters) {
with(as.list(c(state, parameters)), {
if (N > 0) {
dN <- r * N - h
} else {
dN <- 0
}
list(c(dN))
})
}

#Define the state variables, parameters, and times

parameters <- c(r = 0.23/7, h = 1)
state <- c(N = starting_area_s2)
times <- 0:50 # this is now time in days!

#Run and save the model

exp_harvest_sim_s2 <- ode(y = state, times = times, func = Exponential_harvest, parms = parameters)

exp_harvest_sim_s2

ggplot(aes(x = time, y = N), data = as.data.frame(exp_harvest_sim_s2)) + geom_line()


#Growth with harvest, harvest would start after week 9 - this is if the contractor does not work weekends

Exponential_harvest_wknd <- function(t, state, parameters) {
with(as.list(c(state, parameters)), {
if (N > 0) {
if (t %% 7 < 5) {
dN <- r * N - h
} else {
dN <- r * N
}
} else {
dN <- 0
}
list(c(dN))
})
}

#Run the model

parameters <- c(r = 0.23/7, h = 1)
state <- c(N = starting_area_s2)
times <- 0:50 # this is now time in days!

exp_harvest_wknd_sim_s2 <- ode(y = state, times = times, func = Exponential_harvest_wknd, parms = parameters)

exp_harvest_wknd_sim_s2

#Plot the model

ggplot(aes(x = time, y = N), data = as.data.frame(exp_harvest_wknd_sim_s2)) + geom_line()
```

If clearing was started immediately after the council meeting, 2 weeks away, it could be completed in 5 days, leaving an extra $5,000 in the budget. This means we could 

##Scenario 3: Scenario 2 with a 1 week delay

Exploring how many days it would take if the contractor could not begin clearing until week 3

```{r}
#Exponential model function
Exponential <- function(t, state, parameters) {
with(as.list(c(state, parameters)), {
dN <- r * N
list(c(dN))
})
}

#Define the state variables, parameters, and times

parameters <- c(r = 0.23)
state <- c(N = 3) # We specify the initial values here
times <- 0:3 #3 weeks

#Run and save the exponential

exponential_sim_s3 <- ode(y = state, times = times, func = Exponential, parms = parameters)

starting_area_s3 <- as.numeric(exponential_sim_s3[4,2])

#Growth with harvest, harvest would start after week 2 - this is if the contractor works weekends

Exponential_harvest <- function(t, state, parameters) {
with(as.list(c(state, parameters)), {
if (N > 0) {
dN <- r * N - h
} else {
dN <- 0
}
list(c(dN))
})
}

#Define the state variables, parameters, and times

parameters <- c(r = 0.23/7, h = 1)
state <- c(N = starting_area_s3)
times <- 0:50 # this is now time in days!

#Run and save the model

exp_harvest_sim_s3 <- ode(y = state, times = times, func = Exponential_harvest, parms = parameters)

exp_harvest_sim_s3

ggplot(aes(x = time, y = N), data = as.data.frame(exp_harvest_sim_s3)) + geom_line()


#Growth with harvest, harvest would start after week 9 - this is if the contractor does not work weekends

Exponential_harvest_wknd <- function(t, state, parameters) {
with(as.list(c(state, parameters)), {
if (N > 0) {
if (t %% 7 < 5) {
dN <- r * N - h
} else {
dN <- r * N
}
} else {
dN <- 0
}
list(c(dN))
})
}

#Run the model

parameters <- c(r = 0.23/7, h = 1)
state <- c(N = starting_area_s3)
times <- 0:50 # this is now time in days!

exp_harvest_wknd_sim_s3 <- ode(y = state, times = times, func = Exponential_harvest_wknd, parms = parameters)

exp_harvest_wknd_sim_s3

#Plot the model

ggplot(aes(x = time, y = N), data = as.data.frame(exp_harvest_wknd_sim_s3)) + geom_line()
```

The slime could be cleared in 6 days, so we would need to request $6,000 from the committee.


##Scenario 4: Scenario 2 with a 2 week delay

Exploring how many days it would take if the contractor could not begin clearing until week 4

```{r}
#Exponential model function
Exponential <- function(t, state, parameters) {
with(as.list(c(state, parameters)), {
dN <- r * N
list(c(dN))
})
}

#Define the state variables, parameters, and times

parameters <- c(r = 0.23)
state <- c(N = 3) # We specify the initial values here
times <- 0:4 #4 weeks

#Run and save the exponential

exponential_sim_s4 <- ode(y = state, times = times, func = Exponential, parms = parameters)

starting_area_s4 <- as.numeric(exponential_sim_s4[5,2])

#Growth with harvest, harvest would start after week 2 - this is if the contractor works weekends

Exponential_harvest <- function(t, state, parameters) {
with(as.list(c(state, parameters)), {
if (N > 0) {
dN <- r * N - h
} else {
dN <- 0
}
list(c(dN))
})
}

#Define the state variables, parameters, and times

parameters <- c(r = 0.23/7, h = 1)
state <- c(N = starting_area_s4)
times <- 0:50 # this is now time in days!

#Run and save the model

exp_harvest_sim_s4 <- ode(y = state, times = times, func = Exponential_harvest, parms = parameters)

exp_harvest_sim_s4

ggplot(aes(x = time, y = N), data = as.data.frame(exp_harvest_sim_s4)) + geom_line()


#Growth with harvest, harvest would start after week 9 - this is if the contractor does not work weekends

Exponential_harvest_wknd <- function(t, state, parameters) {
with(as.list(c(state, parameters)), {
if (N > 0) {
if (t %% 7 < 5) {
dN <- r * N - h
} else {
dN <- r * N
}
} else {
dN <- 0
}
list(c(dN))
})
}

#Run the model

parameters <- c(r = 0.23/7, h = 1)
state <- c(N = starting_area_s4)
times <- 0:50 # this is now time in days!

exp_harvest_wknd_sim_s4 <- ode(y = state, times = times, func = Exponential_harvest_wknd, parms = parameters)

exp_harvest_wknd_sim_s4

#Plot the model

ggplot(aes(x = time, y = N), data = as.data.frame(exp_harvest_wknd_sim_s4)) + geom_line()
```

With a two week delay, the slime could be cleared in 8 days if the contractor works weekends, which would cost $10000.If the contractor does not work weekends, then it would take 10 days, with a cost of 10,000 dollars.